Nearest Neighbour Methods for Length of Stay Prediction

### 2015-03-08 papers/paper.tex
Add correct references to tables and figures to the discussion

\subsection{Comparison of Feature Selection Methods}
The best accuracy and AUC results for
each classifier resulted from a reduced feature set obtained through a
particular feature selection method. Out of 20 combinations of classifiers
and discretisation (the 10 classifiers with and 10 without
discretisation), the C4.5 wrapper method resulted in the best
accuracy for 7 of these combinations, followed by 5 using information gain
and 4 using the correlation coefficient and very few for the other methods.
\texttt{TODO: recount the numbers in this paragraph.}

In terms of AUC, we
find that the correlation coefficient and the information gain are the feature
selectors that give the best AUC for most of the classifiers, and perform
equally well when used in conjunction with logistic regression and SVMs.
Interestingly, although the C4.5
wrapper method selects features which allow classifiers to achieve good
accuracy, only in 2 out of the 20 combinations of classifiers did it give the
best AUC result out of all the feature selectors.

Note that regardless of whether we consider accuracy or AUC to be more
important in evaluating classifiers, neither the baseline
feature set from Dinh et al. \cite{Dinh2013a} nor the features suggested by
the expert yielded better
results than automatic feature selection in all but \texttt{two?} cases. Neither
feature selection method produced the best AUC result for any classifier.
This is a surprising result because intuitively -- and in the literature -- it
has been stated that in a highly specialised field such as medicine, the domain
experts would be best-equipped to make judgements about which features to
use \cite{Witten2005}, and these should give reasonable results. However,
our results show that in attempting to classify patients according to their
LOS, we should consider both manual and automatic approaches.

@@

\subsection{Comparison of Classifiers}
In terms of classification accuracy, we did not find a lot of variation
between all classifiers, with Zero-R producing 66.91\% accuracy and 77.81\%
being the best we achieved -- an improvement of just over 10\%. The AUC of
the 11 classifiers we tested ranged from 0.498 with Zero-R to 0.846 with
logistic regression. Logistic regression, the \textit{de facto} method
used in LOS classification, performed consistently better than the others
across all feature
selection methods, but only when the feature set was not heavily reduced by
the feature selector: in these cases, such as the results from Figure
\ref{fig:tr-nothreshold-cfs-acc} showing classifier performance with features
selected by C4.5 and nearest
neighbour methods have higher accuracy than logistic regression. This is also
apparent from the graphs in Figure \ref{fig:tr-threshold}: for both
feature selection methods, as we increase the threshold, logistic regression
drops in performance after the initial few thresholds and is outperformed by
C4.5 and the various nearest neighbour classifiers ($k$-NN with 1 and 20
neighbours and K*), as well as our Ranked Distance algorithm.
This is true for both accuracy and AUC.

>>>>

\subsection{Comparison of Feature Selection Methods}
The best accuracy and AUC results for
each classifier resulted from a reduced feature set obtained through a
particular feature selection method. Out of 14 combinations of classifiers
and discretisation (the 7 classifiers with and 7 without
discretisation), the C4.5 wrapper method resulted in the best
accuracy for 5 of these combinations, followed by 5 using information gain,
2 using the correlation coefficient and very few for the other methods.

In terms of AUC, we
find that the correlation coefficient and the information gain are the feature
selectors that give the best AUC for most of the classifiers, and perform
equally well when used in conjunction with logistic regression and SVMs.
Interestingly, correlation coefficient as a feature selector produced the
best AUC results for 6 out the 14 combinations, compared to only 2 when we
considered accuracy instead.

Note that regardless of whether we consider accuracy or AUC to be more
important in evaluating classifiers, neither the baseline
feature set from Dinh et al. \cite{Dinh2013a} nor the features suggested by
the expert yielded better
results than automatic feature selection in all cases. Neither
feature selection method produced the best AUC result for any classifier.
This is a surprising result because intuitively -- and in the literature -- it
has been stated that in a highly specialised field such as medicine, the domain
experts would be best-equipped to make judgements about which features to
use \cite{Witten2005}, and these should give reasonable results. However,
our results show that in attempting to classify patients according to their
LOS, we should consider both manual and automatic approaches.

@@

\subsection{Comparison of Classifiers}
In terms of classification accuracy, we did not find a lot of variation
between all classifiers, with Zero-R producing 66.91\% accuracy and 77.81\%
being the best we achieved -- an improvement of just over 10\%. The AUC of
the 11 classifiers we tested ranged from 0.498 with Zero-R to 0.846 with
logistic regression. Logistic regression, the \textit{de facto} method
used in LOS classification, performed consistently better than the others
across all feature
selection methods, but only when the feature set was not heavily reduced by
the feature selector: in these cases, such as the results from Figure
\ref{fig:tr-nothreshold-wrapper-acc} and \ref{fig:tr-nothreshold-wrapper-auc}
showing classifier performance with features
selected by C4.5 and nearest
neighbour methods have higher accuracy than logistic regression. This is also
apparent from the graphs in Figure \ref{fig:tr-threshold}: for both
feature selection methods, as we increase the threshold, logistic regression
drops in performance after the initial few thresholds and is outperformed by
C4.5 and the various nearest neighbour classifiers ($k$-NN with 1 and 20
neighbours and K*), as well as our Ranked Distance algorithm.
This is true for both accuracy and AUC.
